Analyzing Buildlogs Using Programming by Example

### 2019-06-14 paper/paper.tex
reintegrate some bullet points from old draft

@@

@@

\mention{sth about IR / paragraph retrieval}

@@

>>>>

\plan{improving time developers take to understand buildlogs, vasallo by summarizing relevant information in java/maven buildlogs and augmenting with links to related stack overflow  posts, amar et al. (by removing lines that appear both in passing and failing buildlogs and therefore) reducing the lines needed to be inspected, information retrieval techniques to identify most important lines for investigation and categorize the build failure cause (-> automatic rerun because of environmental failure?)
}

@@

\plan{Le et al. developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses \todo{inductive - explain or throw out} synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code

we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction
}

@@

\plan{characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}}

\mention{sth about IR / paragraph retrieval}
\plan{practices from information retrieval, cutting into lines or paragraphs, calculating similarities through methods xy}

@@

\plan{capabilities: give example extractions \& limitations}
